Survey 2 : Dependent Variable Graphs

### 2022-04-10 module2/module2DVgraphs.Rmd
combined dataset for DV graphs and finalised headings

## Original Dataset
```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")

module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
module2 %>%
  filter(!row_number() %in% c(1,2))

@@

## Coded Dataset

@@

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))

codedmodule2
```

## Q1. Below is a list of various centrally managed sources of energy. How risky are each of these energy technologies according to you?  Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky

@@

risksumcentral <- codedmodule2 %>%
  dplyr::select(!starts_with(c("RISKY_IND")))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Risky) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedrisk.', names(.))) %>%
  dplyr::rename(technology= perceivedrisk.technology)

@@

## Q2. Following is a list of various individually or community-owned and managed sources of energy. How risky are each of these energy technologies according to you? Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.

@@

risksumIND <- codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Risky) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedrisk.', names(.))) %>%
  dplyr::rename(technology= perceivedrisk.technology)

@@

## Q3. Following is a list of centrally managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?

@@

bensumcentral <- codedmodule2 %>%
  dplyr::select(!starts_with(c("Ben_IND")))%>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Ben) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  dplyr::rename(technology= perceivedbenefit.technology)

@@

## Q4. Following is a list of various individually or community owned and managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?

@@

bensumIND <- codedmodule2 %>%
  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Ben) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  dplyr::rename(technology= perceivedbenefit.technology)

@@

 center_barplot%>% 
  ggplot(aes(x=technology, y= mean, fill =  (factor(center_barplot$level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
  geom_bar(stat="identity", position=position_dodge())+
#geom_errorbar(aes(ymin= mean - sd, ymax= mean + sd), width =.2, position=position_dodge(.9))+
  ylim(0,4)+
  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
  labs(y = "Mean Values", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies")+
  coord_flip()

@@

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")

module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

@@

@@

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))
```

```{r, eval=TRUE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)

```{r, eval =TRUE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5)))

#coded dependent variables for module 1 livelihood and income security survey

```{r}

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2

numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")

joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))

## Q1. Below is a list of various centrally managed sources of energy. How risky are each of these energy technologies according to you?  Please tell me whether you see each technology as: not at all risky(1), slightly risky(2), moderately risky(3), very risky(4), or extremely risky(5)

@@

risksumcentral <- joineddf %>%
  dplyr::select(!starts_with(c("RISKY_IND")))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Risky) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedrisk.', names(.))) %>%
  dplyr::rename(technology= perceivedrisk.technology)

@@

## Q2. Following is a list of various individually or community-owned and managed sources of energy. How risky are each of these energy technologies according to you? Please tell me whether you see each technology as: not at all risky(1), slightly risky(2), moderately risky(3), very risky(4), or extremely risky(5).

prefix IND stands for individually or community-owned and managed.

@@

risksumIND <- joineddf %>%
  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Risky) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedrisk.', names(.))) %>%
  dplyr::rename(technology= perceivedrisk.technology)

@@

## Q3. Following is a list of centrally managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial(1), slightly beneficial(2), moderately beneficial(3), very beneficial(4), or extremely beneficial(5)?

@@

bensumcentral <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND")))%>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Ben) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  dplyr::rename(technology= perceivedbenefit.technology)

@@

## Q4. Following is a list of various individually or community owned and managed sources of energy. How beneficial are each of these according to you? Please tell me whether you see each technology as: not at all beneficial(1), slightly beneficial(2), moderately beneficial(3), very beneficial(4) or extremely beneficial(5) ?

prefix IND stands for individually or community-owned and managed.

@@

bensumIND <- joineddf %>%
  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  dplyr::select(-rowname, -Ben) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  dplyr::rename(technology= perceivedbenefit.technology)

@@

 center_barplot%>% 
  ggplot(aes(x=technology, y= mean, fill =  (factor(center_barplot$level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
  geom_bar(stat="identity", position=position_dodge())+

#geom_errorbar(aes(ymin= mean - sd, ymax= mean + sd), width =.2, position=position_dodge(.9))+
  ylim(0,4)+
  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
  labs(y = "Mean Values", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies")+
  coord_flip()

@@

Prefix IND stands for individually or community-owned and managed.
